---
title: "Capstone Proposal"
author: "Donnie Meyer"
date: "October 1, 2018"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
setwd("/home/donniemeyer32085/git/capstone/solar_surveys/")
ACGPS_Viz <- read_csv("ACGPS_Viz.csv")
```


## Project Proposal

#### What is the problem you want to solve?

I want to understand what factors play prominent roles for influencing households to adopt roof top solar. There are many reasons why consumers adopt, and choose not to rooftop adopt solar. For example, some adopt for financial gain while others adopt for environmnetal reasons. I would like to see on average, which factors played a larger role for adoption. I would also like to see if any demographic groups adopted roof top solar at higher rates. Understanding the roof top solar adoption characteristic is am exteremly worth while endevour. Rising energy prices, climate change, and lack of jobs such as the coal industry in the US have put tremenduoes pressure on the working class as well as there political representitives. Roof top solar could help solve a large part of the problem by providing clean affordable enegy as well as create new jobs through out the country.

#### Who is your client and why do they care about this problem? In other words, what will your client DO or DECIDE based on your analysis that they wouldn’t have otherwise?

I beleieve solar intallation firms would be interested in this information as it would help them pinpoint marketing strategies to increase sales. If there are households who are on the fence about adopting rooftop solar that have common characterictics to households who have already adopted, advertising to them could help them make the switch. I also beleieve government and policy makers would like to understand groups who may adopt solar, but lack the financial resoucres to do so. This could help policy makers craft more effective incentive based policies and created an economic environment where these holds would have the oppurtunity to adopt solar.

#### What data are you going to use for this? How will you acquire this data?

The data I will be using is a survey data set where all features are catagorical, i.e no continuos variabales. The name of the data set is "Understanding the Evolution of Customer Motivations and Adoption Barriers in Residential Solar Markets: Survey Data" and it has been made public from the National Renewable Energy Laboratory (NREL). 

The data comprises of three surveys, an adopter survey, a considerer survey, and a general population survey. The adopter survey is constarined to households who have adopted roof top solar, the considrer survey is constrained to househholds who have seriously considered adopting solar but have yet to do so, and the general population survey is constrained to households who have not adopted roof top solar. The surveys were conducted in four states in the US which were California, Arizona, New York, and New Jeresey.

#### In brief, outline your approach to solving this problem (knowing that this might change later).

The survey data set has many catagorical varibles that may be useful as explanatory varibles. I currently have a binary dependent variable called "HAVESOLAR" in both tf I append these two data sets the variable is equal to 1 for currenlty have solar, and eqaul to zero if they currenlty do not have solar. Therefor, I can use a logistic regression to model what depednet factor variables play a prominent role influencing considrers to ultimitly make the switch. 

I will have the abilty to look at contigency tables to gain better insight into the distributions bewteen solar and non solar adopters as well as visluizations. For an example I included a table and graph below. 

If time permits I would like to perform a cluster analysis to the data set. 

```{r}
### STATE VARIABLE ###
ACGPS_Viz$STATE <- recode(ACGPS_Viz$STATE, 
                           `1` = "New_Jersey", 
                           `2` = "New_York", 
                           `3` = "Arizona", 
                           `4` = "California",
                           `92` = "Other")
#table of states and solar
tab_state_solar <- as.tibble(table(ACGPS_Viz$STATE, ACGPS_Viz$HAVESOLAR))
colnames(tab_state_solar) <- c("STATE", "HAVESOLAR", "COUNT")
#table with proportions
tab_state_solar_prop <- tab_state_solar %>% 
  mutate(Prop_SOLAR = COUNT/sum(COUNT)) %>%
  arrange(desc(Prop_SOLAR))
tab_state_solar_prop

```

```{r pressure, echo=FALSE}
#the bar graph is hard to get information from, use position = fill in geom_col
ggplot(data = tab_state_solar_prop, mapping = aes(x = STATE, y = Prop_SOLAR, fill = HAVESOLAR)) + 
  geom_col(color = "black", position = "fill") +
  coord_flip()
```

#### What are your deliverables? Typically, this would include code, along with a paper and/or a slide deck.

The deliverables will be a written report in rmarkdown in addition to slides for presentation or a blog posting on wordpress. Code will be available through github. 
